---
title: "Homework-3"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

# Question 5.1

**Using crime data from the file uscrime.txt
(<http://www.statsci.org/data/general/uscrime.txt>, description at
<http://www.statsci.org/data/general/uscrime.html>), test to see whether
there are any outliers in the last column (number of crimes per 100,000
people). Use the grubbs.test function in the outliers package in R.**

**Import Packages**

```{r}
library(outliers)
```

**Load Data**

```{r}
data = read.table("C:/Users/Admin/Desktop/MM/Homework 3/uscrime.txt",
                  stringsAsFactors = FALSE, 
                  header = TRUE) 
head(data)
```

**Visualize Data Distribution**

```{r}
# Histogram
hist(data[,'Crime'], 
     main = 'Crime Rate Distribution',
     xlab = 'Crime Rate',
     breaks = nrow(data),
     xlim = c(min(data[,'Crime']),
              max(data[,'Crime'])))

# Boxplot
boxplot(data[,'Crime'])
```

## 2-tailed test

```{r}
# Test for outliers on opposite tails of data distribution
grubbs.test(data[,'Crime'],type=11)
```

2-tailed test returns with p-value = 1, meaning null hypothesis of both
342 and 1993 are not outliers is not rejected.

## 1-tailed test

```{r}
# Testing negative tail end outlier
grubbs.test(data[,'Crime'],type=10, opposite = TRUE)
```

With p-value = 1, point 342 is not considered as an outlier.

```{r}
# Testing positive tail end outlier
grubbs.test(data[,'Crime'],type=10, opposite = FALSE)
```

Depending on p-value threshold selected (0.1 or 0.05) we could choose to
flag data point 1993 as an outlier or not.

```{r}
# If we were to exclude data point 1993 and run the test for outlier again
data.new = data[-which.max(data[,'Crime']),]
grubbs.test(data.new[,'Crime'],type=10, opposite = FALSE)
```

Data point 1969 with p-value \< 0.05 could also be considered as an
outlier.

```{r}
# Removing data point 1969 
data.new = data.new[-which.max(data.new[,'Crime']),]
grubbs.test(data.new[,'Crime'],type=10, opposite = FALSE)
```

Data point 1674 with p-value \> 0.05 and 0.1, not an outlier according
to Grubbs test.

**Visualize Data Distribution after removing outlier**

```{r}
b = min(c(data[,'Crime'], data.new[,'Crime']))
e = max(c(data[,'Crime'], data.new[,'Crime']))
ax = pretty(b:e, n=12)

hist1 = hist(data[,'Crime'], breaks = ax, plot = FALSE)
hist2 = hist(data.new[,'Crime'], breaks = ax, plot = FALSE)

c1 = rgb(0, 0, 255, max = 255, alpha = 70)
c2 = rgb(0, 255, 0, max = 255, alpha = 70)

plot(hist1, col = c1)
plot(hist2, col = c2, add = TRUE)
```

\newpage

# Question 6.1

**Describe a situation or problem from your job, everyday life, current
events, etc., for which a Change Detection model would be appropriate.
Applying the CUSUM technique, how would you choose the critical value
and the threshold?**

In banks, cash movement and liquidity in all aspects of businesses are
highly monitored to prevent potential bribery, corruption, fraud,
terrorism financing, or even rogue trading. Retail banking in
particular, it is important to track changes in transfer of funds across
accounts, especially overseas. A change detection model in this
circumstance would be insightful to help highlight these behaviors.
Since there is little to no cost in a false positive detection, and on
the other hand huge implications for not detecting such cases, it would
make sense for the model to be fairly sensitive to large changes with
low threshold level and a lower C value.

\newpage

# Question 6.2

1.  **Using July through October daily-high-temperature data for Atlanta
    for 1996 through 2015, use a CUSUM approach to identify when
    unofficial summer ends (i.e., when the weather starts cooling off)
    each year. You can get the data that you need from the file
    temps.txt or online, for example at
    <http://www.iweathernet.com/atlanta-weather-records> or
    <https://www.wunderground.com/history/airport/KFTY/2015/7/1/CustomHistory.html>
    . You can use R if you'd like, but it's straightforward enough that
    an Excel spreadsheet can easily do the job too.**
2.  **Use a CUSUM approach to make a judgment of whether Atlanta's
    summer climate has gotten warmer in that time (and if so, when).**

Please refer to excel sheet.
