---
title: "Homework-8"
output: 
  pdf_document: 
    latex_engine: xelatex
---

# Question 11.1

**Using the crime data set uscrime.txt from Questions 8.2, 9.1, and 10.1, build a regression model using:**

**1. Stepwise regression**

**2. Lasso**

**3. Elastic net**

**For Parts 2 and 3, remember to scale the data first -- otherwise, the regression coefficients will be on different scales and the constraint won't have the desired effect.**

**For Parts 2 and 3, use the glmnet function in R.**

**Notes on R:**

-   **For the elastic net model, what we called λ in the videos, glmnet calls "alpha"; you can get a range of results by varying alpha from 1 (lasso) to 0 (ridge regression) [and, of course, other values of alpha in between].**

-   **In a function call like glmnet(x,y,family="mgaussian",alpha=1) the predictors x need to be in R's matrix format, rather than data frame format. You can convert a data frame to a matrix using as.matrix -- for example, x \<- as.matrix(data[,1:n-1])**

-   **Rather than specifying a value of T, glmnet returns models for a variety of values of T.**

## 1. Stepwise

```{r}
rm(list=ls())
set.seed(42069)

library(caret)
library(glmnet)

data = read.table("C:/Users/Admin/Desktop/MM/Homework 8/uscrime.txt",
                  stringsAsFactors = FALSE, 
                  header = TRUE)
head(data)

# exclude scaling binary and target variable
data.scaled = as.data.frame(scale(data[,c(1,3,4,5,6,7,8,9,10,11,12,13,14,15)]))
data.scaled = cbind(data.scaled, data[,c(2,16)])
head(data.scaled)

# backwards stepwise
control = trainControl(method = 'repeatedcv',
                       number = 5,
                       repeats = 5)
model.backwards = train(Crime~.,
                        data = data.scaled,
                        method = 'lmStepAIC',
                        direction = 'backward',
                        trControl = control)
model = lm(Crime~M+Ed+Po1+U1+U2+Ineq+Prob, # variables from backwards stepwise
           data = data.scaled)
summary(model)

# forward stepwise
model.forward = train(Crime~.,
                      data = data.scaled,
                      method = 'glmStepAIC',
                      direction = 'forward',
                      trControl = control)
model = lm(Crime~Po1+Ineq+Ed+Prob+M, # variables from forward stepwise
           data = data.scaled)
summary(model)
```

\newpage

## 2. Lasso

```{r}
model.lasso = cv.glmnet(x = as.matrix(data.scaled[,-16]),
                        y = as.matrix(data.scaled$Crime),
                        alpha = 1, # 1 for lasso
                        nfolds = 5,
                        type.measure = 'mse',
                        family = 'gaussian')
coef(model.lasso, s = model.lasso$lambda.min)

# dev.ratio = fraction of deviance explained, r squared, 1-dev/nulldev
r.lasso = model.lasso$glmnet.fit$dev.ratio[which(model.lasso$glmnet.fit$lambda == model.lasso$lambda.min)]
r.lasso
```

\newpage

## 3. Elastic Net

```{r}
dev = list()
for (i in 0:10){ # 0 for ridge, 1 for lasso
  model.elastic = cv.glmnet(x = as.matrix(data.scaled[,-16]),
                            y = as.matrix(data.scaled[,16]),
                            alpha = i/10,
                            nfolds = 5,
                            type.measure = 'mse',
                            family = 'gaussian')
  dev[i] = model.elastic$glmnet.fit$dev.ratio[which(model.elastic$glmnet.fit$lambda == model.elastic$lambda.min)]
}

# run model with best alpha identified
model.elastic = cv.glmnet(x = as.matrix(data.scaled[,-16]),
                          y = as.matrix(data.scaled[,16]),
                          alpha = which.max(dev)/10, # best alpha
                          nfolds = 5,
                          type.measure = 'mse',
                          family = 'gaussian')
coef(model.elastic, s = model.elastic$lambda.min)
r.elastic = model.lasso$glmnet.fit$dev.ratio[which(model.lasso$glmnet.fit$lambda == model.lasso$lambda.min)]
r.elastic
```
